\documentclass[letterpaper,11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{baskervillef}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{needspace}

% Define custom colors
\definecolor{sectioncolor}{RGB}{0,0,0}
\definecolor{linkcolor}{RGB}{0,0,0}
\definecolor{footergrey}{gray}{0.3}

\fancypagestyle{plain}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[L]{\color{footergrey}\footnotesize Updated: \today}
    \fancyfoot[R]{\color{footergrey}\footnotesize Page \thepage\ of \text{\color{footergrey}\pageref{LastPage}}}
}
\pagestyle{plain}

% Suppress mid-word hyphenation but allow breaks at existing hyphens
\hyphenpenalty=10000
\tolerance=2000
\emergencystretch=1em

% Section formatting - large headers like the full CV
\titleformat{\section}{
    \normalfont\large\bfseries\color{sectioncolor}
}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{11pt}{5pt}

% Entry with wrappable left column and atomic right-aligned date (stays on first line)
\newcommand{\cvEntry}[2]{%
    \item \parbox[t]{\dimexpr\linewidth-6em\relax}{\raggedright #1}\hfill\mbox{#2}%
}

\begin{document}

% Header
\begin{center}
    {\Large\textbf{YINING WU}}\vspace{4pt}\\
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ll}
    \begin{minipage}[t]{0.6\textwidth}
    \begin{flushleft}
    \small University of Tennessee\\
    \small Department of Agricultural and Resource Economics\\
    \small Baker School of Public Policy and Public Affairs\\
    \end{flushleft}
    \end{minipage}
    &
    \begin{minipage}[t]{0.35\textwidth}
    \begin{flushright}
    \small \href{mailto:ywu96@utk.edu}{ywu96@utk.edu}\\
    \small (+1) 614-906-1547\\
    \small \href{https://yiningwu510.github.io}{yiningwu510.github.io}
    \end{flushright}
    \end{minipage}
    \end{tabular*}
\end{center}

\section{ACADEMIC APPOINTMENTS}
\begin{itemize}[leftmargin=1em, itemsep=3pt, parsep=0pt, topsep=3pt]
    \cvEntry{\textbf{Post-Doctoral Research Associate}, University of Tennessee}{2025--present}
    \item[] \small Department of Agricultural and Resource Economics; Baker School of Public Policy and Public Affairs
\end{itemize}

\section{EDUCATION}
\begin{itemize}[leftmargin=1em, itemsep=3pt, parsep=0pt, topsep=3pt]
    \cvEntry{\textbf{Ph.D.} Agricultural, Environmental, and Development Economics, The Ohio State University}{2025}
    \cvEntry{\textbf{M.S.} Agricultural, Environmental, and Development Economics, The Ohio State University}{2022}
    \cvEntry{\textbf{B.S. (Hons.)} Agricultural and Forestry Economics and Management, China Agricultural University}{2020}
    \cvEntry{\textbf{Exchange Student (Hons.)} Agriculture Economics, Oklahoma State University}{2018}
\end{itemize}

\section{FIELDS OF INTEREST}
Environmental and Resource Economics, Agricultural Economics, and Applied Econometrics

\section{PEER-REVIEWED PUBLICATIONS}
\begin{itemize}[leftmargin=1em, itemsep=4pt, parsep=0pt, topsep=3pt]
    \item Stanley, P. L., et al.\ ``Merging Rigor and Relevance in Grazingland Research: A Comprehensive Social-Ecological Monitoring Approach,'' \textit{Carbon Balance and Management} 21(1), 67 (2026). \\
    \href{https://doi.org/10.1186/s13021-026-00431-7}{https://doi.org/10.1186/s13021-026-00431-7}
    \item Wu, Y., Davis, E. C., \& Sohngen, B. L. ``Crop Rotation and the Impact on Soil Carbon in the US Corn Belt,'' \textit{Carbon Balance and Management} 20(1), 6 (2025). \\
    \href{https://doi.org/10.1186/s13021-025-00293-5}{https://doi.org/10.1186/s13021-025-00293-5}
\end{itemize}

\section{WORKING PAPERS}
\begin{itemize}[leftmargin=1em, itemsep=3pt, parsep=0pt, topsep=3pt]
    \item ``Waters of Change: Estimating Spatiotemporal Welfare Losses from Recurring Harmful Algal Blooms in Lake Erie Recreational Fishing'' (with F. Lupi and B. Sohngen)
    \item ``Who Stays, Who Leaves? Recreational Fishing Responses to Harmful Algal Blooms in Lake Erie'' (with B. Sohngen and S. Ludsin)
\end{itemize}

\section{WORK IN PROGRESS}
\begin{itemize}[leftmargin=1em, itemsep=3pt, parsep=0pt, topsep=3pt]
    \item ``Do Cow-Calf Producers Avoid Uncertain Conservation Payments? Measuring Risk Preferences for Ecosystem Service Contracts''
    \item ``Optimizing Grazing Management for Profit and Ecosystem Services: An Integrated Biogeochemical-Economic Model''
\end{itemize}

\section{BOOK CHAPTERS}
\begin{itemize}[leftmargin=1em, itemsep=3pt, parsep=0pt, topsep=3pt]
    \item Wu, Y. (2018). ``The Development of Rural Social Security System from 1978 to 2018.'' In Li, J., et al. (Eds.), \textit{Social Changes in Rural Area since 1978}. Beijing, China: China Agriculture Press, 393--404.
\end{itemize}

\newpage

\section{TEACHING EXPERIENCE}
\begin{itemize}[leftmargin=1em, itemsep=4pt, parsep=0pt, topsep=3pt]
    \item \textbf{Instructor} (The Ohio State University): Environmental \& Natural Resource Economics (AEDECON 4310, Summer 2024)
    \item \textbf{Lab Instructor} (The Ohio State University): Introduction to Sustainability (ENR/AEDECON 2501, Fall 2024); Applied Econometrics II (AEDECON 7140, Spring 2022)
    \item \textbf{Teaching Assistant} (The Ohio State University): Environmental \& Natural Resource Economics (AEDECON 4310, Spring 2024); Strategic Management (AEDECON 4106, Spring 2022); International Economic Development (AEDECON/PUBAFRS 4535, Fall 2021)
\end{itemize}

\section{PRESENTATIONS}
\begin{itemize}[leftmargin=1em, itemsep=1pt, parsep=0pt, topsep=2pt]
    \item 3rd Annual Postdoc Research Symposium. Knoxville, TN (March 2026)
    \item W5133 Multi-State Project Annual Meeting. Boise, ID (February 2026)
    \item AREC Departmental Seminar. Knoxville, TN (October 2025)
    \item Camp Resources XXXI. Asheville, NC (August 2025)
    \item Association of Environmental and Resource Economists Summer Conference. Santa Ana Pueblo, NM (May 2025)
    \item Agricultural and Applied Economics Association Annual Meeting. New Orleans, LA (July 2024)
    \item Lake Erie -- Inland Waters Annual Research Review. Columbus, OH (December 2023)
    \item Interdisciplinary Water Research Symposium. Columbus, OH (November 2023)
    \item Agricultural and Applied Economics Association Annual Meeting. Washington D.C. (July 2023)
    \item Association of Environmental and Resource Economists Summer Conference. Portland, ME (June 2023)
    \item U.S. Department of Agriculture Carbon Sinks Modelling Meeting. Atlanta, GA (September 2022)
\end{itemize}

\section{PROFESSIONAL SERVICE}
\begin{itemize}[leftmargin=1em, itemsep=3pt, parsep=0pt, topsep=3pt]
    \item Referee for \textit{Carbon Balance and Management} and \textit{Catena}
    \item Abstract reviewer for \textit{Association of Environmental and Resource Economists} Summer Conference
    \item Proposal reviewer for CFAES Internal Grants Program
\end{itemize}

\section{HONORS AND FELLOWSHIPS}
\begin{itemize}[leftmargin=1em, itemsep=2pt, parsep=0pt, topsep=2pt]
    \cvEntry{Postdoc Travel Award, University of Tennessee}{2026}
    \cvEntry{AERE Graduate Student and Postdoc Travel Scholarship}{2025}
    \cvEntry{Career Development Grant, The Ohio State University}{2023}
    \cvEntry{2nd Prize in Oral Presentation Student Competition, Interdisciplinary Water Research Symposium}{2023}
    \cvEntry{University Fellowship, The Ohio State University}{2020--2021}
    \cvEntry{University Distinguished Thesis Award, China Agricultural University}{2020}
    \cvEntry{Beijing Outstanding Student Award, Beijing Municipal Education Commission}{2020}
    \cvEntry{First Prize in Xiji-An Agricultural Economics Research, China Agricultural University}{2018}
    \cvEntry{President's Honor Roll, Oklahoma State University}{2018}
\end{itemize}

\section{OTHER INFORMATION}
\noindent\textbf{Technical Skills:} R, Stata, Python, HPC, Matlab, ArcGIS, QGIS, LaTeX\\
\textbf{Languages:} English (fluent), Chinese (native)

\end{document}
